### 2021-03-03 Dokumentation/paper.tex
Added Documentation

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\begin{document}
\title{Merging Plans of Robots in the asprilo Framework}

\author{Adrian Salewsky}

\authorrunning{A. Salewsky}

\institute{University of Potsdam}

\maketitle

\begin{abstract}
The asprilo framework was created to make plans for robots in a warehouse. It uses the language Answer Set Programming
which is a good choice for such a problem because this language was made for solving NP-hard problems. The solution works 
well for a small number of robots but at some point the computation time gets too high. This is why the idea came up to create plans
for a small number of robots and then combine the plans to get a working solution. This paper shows my approach on how to solve
the plan merging problem.
\end{abstract}

\section{Introduction}
The asprilo framework is used to make plans for robots in a warehouse, i.e. when does a robot pick up or shelf or when does a robot move which way. 
It uses the language Answer Set Programming (ASP). Since there is no order in which ASP computes things, the predicates which describe the actions of robots and
the positions of objects contain an argument $T$ which declares at which time step the predicate holds. This project was done in the M-domain of the asprilo framework.
In the M-domain, the goal is that every shelf has a robot on the same node at the last time step (the last time step is called horizon). This domain simplifies the framework 
to Multi-Agent Path Finding (MAPF). The framework works well for a small number of robots but for a high number of robots, the computation time gets too high. This is
why the plan came up to combine plans with a small number of robots to a plan with all the robots. During the combining of these plans, all the conflicts that arise between 
robots must be solved. This paper shows my approach on how to solve this plan merging problem in ASP. In the following section, I will show my general idea on how to solve 
conflicts. In the section after that, I will show my ASP encoding and explain its functions. Section 4 contains the comparison of my approach with that of other groups that have
been working on the same project. I will end my paper with a conclusion.

\section{Idea}
The main idea behind my solution is that every time a conflict arises, one of the robots participating in the conflict randomly changes his movement during that time step and pushes his original plan back. 
To do that, the program needs to detect the conflicts and choose a robot who has to solve the conflict by generating a new move. The problem that arises is that
there is no option to overwrite predicates in ASP. Therefore, a new argument was needed for every predicate describing a plan. This new argument is called $conflict\_nr$ and 
the higher this argument is in a predicate the newer is the plan containing that predicate. This idea is a very simple approach to solving the problem since it completely adapts the original plan and only
inserts additional moves. This way the resulting solution might not have an optimal move set for every robot but it should be able to theoretically solve any problem instance.

\section{Answer Set Programming Encoding}
\subsection{Initiating Predicates}
- conflict depth \\
- horizon \\
- initiating position ...

\subsection{Conflict Detection and Selection}
- show how its done \\
- talk about minimization \\

\subsection{Conflict Solving}
- show possibilities \\
- show how plan gets changed

\subsection{Integrity Constraints}
- show which ones \\
- talk about efficiency

\subsection{Output}
- show new\_move \\
- show new\_occurs

\subsection{Extra Features}
There are two extra features I have dealt with. The first extra feature is the possibility of declaring that certain robots do not have to change their plan at all.
This is done by adding the predicate $strict\_plan(R\_ID)$ with $R\_ID$ being the ID of a robot. The only thing that gets changed in the encoding is in the conflict detection part:
\begin{verbatim}
conflict(R1,T,A) :- position(R1,C1,T-1,A), position(R1,C2,T,A), position(R2,C2,T,A), 
                    R1!=R2, conflict_nr(A), not strict_plan(R1).
\end{verbatim}
The only things that gets added is that a robot can only have a conflict that he might have to solve if he does not have the predicate $strict\_plan$. It is
the same for the second type of conflict. If two robots have a conflict and they both have strict plans there is no solution for that particular problem. 
This is encoded by using additional integrity constraints:
\begin{verbatim}
:- position(R1,C1,T-1,A), position(R1,C2,T,A), position(R2,C2,T,A), R1!=R2, 
   conflict_nr(A), strict_plan(R1), strict_plan(R2).
\end{verbatim}
The other conflict type looks the same. As this is a very hard constraint and can very easily lead to unsatisfiable problems, I have decided to expend on the idea
to let the user control which robot gets chosen as the one who has to solve the conflict. This brings me to my second feature: Introducing a priority system.
The user can add predicates $priority(R\_ID, P)$ where $R\_ID$ is the ID of a robot again and P is the assigned priority of that robot. 
The solver then always chooses the robot with the lower priority to solve a conflict. If two robots have the same priority, either can be chosen. 
\begin{verbatim}
conflict(R1,T,A) :- position(R1,C1,T-1,A), position(R1,C2,T,A), position(R2,C2,T,A), 
                    R1!=R2, conflict_nr(A), p_priority(R1,P1), 
                    p_priority(R2,P2), P1<=P2.
p_priority(R,P) :- priority(R,P).
p_priority(R,0) :- not priority(R,_), isRobot(robot(R)).						
\end{verbatim}
The second conflict looks like the first one. The reason I change $priority$ to $p\_priority$ is that this way I can introduce a default value. If the user does not choose any priority value for a robot,
the priority gets set to 0. \\
Both features change how the conflict solving robot is chosen. Using them can be useful in certain scenarios, especially the second one, but it should be noted that those features can
easily make an instance unsatisfiable.

\section{Comparison with other approaches}
 - advantages and disadvantages of my approach compared to other approaches based on the benchmarking

\section{Conclusion}
This paper explained my approach on how to solve the plan merging problem for the asprilo framework. The solution is able to solve almost all of the benchmarks with the exception being a very niche 
benchmark that is unlikely to appear in the real world. There are two main problems in my solution. The first is that it is very time inefficient. The second is that the user has to in put the time horizon and
the maximum conflict number. If he does not know it, he will likely take an upper bound which increases the computation time. While those two problems are definitely a major deficit of my solution, the trade-off
is that it is generally usable and it finds a solution with the minimum amount of conflicts needed to solve a problem instance. To avoid the time inefficiency, the user can also take a parallel approach, i.e. combining 
the plans of 2 robots at a time, then combining these plans again and so on. This way, the conflict number of the problem instances is likely lower than when combining all plans at once. This also means that the computation time
is reduced. Another possible usage of this solution is adding new robots to a warehouse where a plan for the other robots already exists. Since only a small number of robots is likely added, the conflict number is probably low
enough to get a solution in an acceptable time. \\
My solution to solving the plan merging problem has a lot of possibilities of getting improved, like time efficiency and taking it to the A-domain of the framework. Nevertheless, it is an approach that solves the problem and could
be used in certain scenarios.

\begin{thebibliography} {6}

\end{thebibliography}

\end{document}

### 2021-03-06 Documentation/paper.tex
Updated documentation

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\begin{document}
\title{Merging Plans of Robots in the asprilo Framework}

\author{Adrian Salewsky}

\authorrunning{A. Salewsky}

\institute{University of Potsdam}

\maketitle

\begin{abstract}
The asprilo framework was created to make plans for robots in a warehouse. It uses the language Answer Set Programming
which is a good choice for such a problem because this language was made for solving NP-hard problems. The solution works 
well for a small number of robots but at some point the computation time gets too high. This is why the idea came up to create plans
for a small number of robots and then combine the plans to get a working solution. This paper shows my approach on how to solve
the plan merging problem.
\end{abstract}

\section{Introduction}
The asprilo framework is used to make plans for robots in a warehouse, i.e. when does a robot pick up or shelf or when does a robot move which way. 
It uses the language Answer Set Programming (ASP). Since there is no order in which ASP computes things, the predicates which describe the actions of robots and
the positions of objects contain an argument $T$ which declares at which time step the predicate holds. This project was done in the M-domain of the asprilo framework.
In the M-domain, the goal is that every shelf has a robot on the same node at the last time step (the last time step is called horizon). This domain simplifies the framework 
to Multi-Agent Path Finding (MAPF). The framework works well for a small number of robots but for a high number of robots, the computation time gets too high. This is
why the plan came up to combine plans with a small number of robots to a plan with all the robots. During the combining of these plans, all the conflicts that arise between 
robots must be solved. This paper shows my approach on how to solve this plan merging problem in ASP. In the following section, I will show my general idea on how to solve 
conflicts. In the section after that, I will show my ASP encoding and explain its functions. Section 4 contains the comparison of my approach with that of other groups that have
been working on the same project. I will end my paper with a conclusion.

\section{Idea}
The main idea behind my solution is that every time a conflict arises, one of the robots participating in the conflict randomly changes his movement during that time step and pushes his original plan back. 
To do that, the program needs to detect the conflicts and choose a robot who has to solve the conflict by generating a new move. The problem that arises is that
there is no option to overwrite predicates in ASP. Therefore, a new argument was needed for every predicate describing a plan. This new argument is called $conflict\_nr$ and 
the higher this argument is in a predicate the newer is the plan containing that predicate. This idea is a very simple approach to solving the problem since it completely adapts the original plan and only
inserts additional moves. This way the resulting solution might not have an optimal move set for every robot but it should be able to theoretically solve any problem instance.

\section{Answer Set Programming Encoding}
\subsection{Pre-Required Predicates}
To solve the problem there are several predicates needed before starting to look for predicates. There are two domain intervals whose upper bounds are constants: $time$ with the constant $horizon$ and $conflict\_nr$ with the constant $c\_nr$.
The constants are chosen at run-time. \\ There are some predicates that have been taken over from the encoding for the asprilo framework: $isRobot(robot(R))$ to check if something is a robot, $position((X,Y))$ to check if the node (X,Y) exists, $direction((X,Y))$ declares the 4 directions a robot can go into and $nextto(C1,D,C2)$ states that you get from the node C1 to the node C2 if you into direction D. \\  
The program expects as input a plan of the form $occurs(object(robot,R),action(move,D),T)$. This is transformed into the predicate $move(R,D,T,0)$. This means that the original plan has the $conflict\_nr$ 0. \\
Another part that has been mostly taken over from the encoding for the framework itself is the declaration of the position predicates:
\begin{verbatim}
position(R,C,0,0) :- init(object(robot,R), value(at,C)).
position(R,C,T,A) :- move(R,D,T,A), position(R,C',T-1,A), nextto(C',D,C).
                  :- move(R,D,T,A), position(R,C ,T-1,A), not nextto(C ,D,_).
position(R,C,T,A) :- position(R,C,T-1,A), not move(R,_,T,A), conflict_nr(A), isRobot(robot(R)), time(T).
\end{verbatim}
The difference is that position also contains an argument A for the $conflict\_nr$. The position only gets changed if a move in the same conflict depth A exists. The inertia rule also got changed accordingly. \\
The last part needed before the conflict solving is the predicate $goal$:
\begin{verbatim}
goal(R,C) :- position(R,C,horizon,0).
:- position(R,C,horizon,_), goal(R,C'), C!=C'.
\end{verbatim}
These rules declare that the last position of the initial plan is the goal position and that there can be no plan where a robot
is not on his goal position at the end. While this does not change the solution itself (the plan always only gets pushed back so the robot always ends on the same node), it improves the solution time. \\

\subsection{Conflict Detection and Selection}
There are two types of conflicts that can appear in a problem instance. The first one is that a robot arrives on a node which is either already occupied by another robot or another robot arrives in the same time step. 
\begin{verbatim}
conflict(R1,T,A)	:- position(R1,C1,T-1,A), position(R1,C2,T,A), position(R2,C2,T,A), R1!=R2, conflict_nr(A).
\end{verbatim}
The predicate $conflict(R,T,A)$ is derived for the two robots participating in the conflict. \\
The second conflict is two robots switching their places:
\begin{verbatim}
conflict(R1,T,A)	:- position(R1,C1,T-1,A), position(R1,C2,T,A), position(R2,C2,T-1,A), position(R2,C1,T,A),
						R1!=R2, conflict_nr(A).
\end{verbatim}
The same predicate is derived for this type of conflict. \\
The program detects all of the conflicts arising in a plan this way. Only one conflict can get solved in each conflict depth, otherwise separate plans get created for each robots. The program chooses one of the conflicts that appeared the earliest.
\begin{verbatim}
1{solving_conflict(R,T,A) : conflict(R,T,A)}1 :- conflict(_,_,A).
:- conflict(_,T,A), solving_conflict(_,T',A), T'>T.
\end{verbatim}
The first rule declares that one conflict is chosen as the $solving\_conflict$ in each conflict depth. The second rule declares that a conflict cannot be chosen as solving conflict if there is a conflict that appears in an earlier time step in the same conflict depth. \\
This conflict selection makes it completely random which robot gets chosen as the one who has to solve the conflict. This could mean that the solver finds a plan where a lot of conflicts arise because of inefficient robot selection. This is why I have chosen to let the solver minimize the number of the conflicts:
\begin{verbatim}
#minimize {1,(R,T,A): solving_conflict(R,T,A)}.
\end{verbatim}
This rules forces the solver to find the most efficient way of selecting robots for the conflict solving.

\subsection{Conflict Solving}
After a robot is chosen as the conflict solver, its plan gets changed. 
\begin{verbatim}
0{move(R,D,T,A+1) : direction(D), nextto(C,D,_)}1 :- solving_conflict(R,T,A), position(R,C,T-1,A).
\end{verbatim}
The solver either chooses that the robot has to wait for this time step or that it moves into a random direction.
In both cases the $conflict\_nr$ has to rise for all robots:
\begin{verbatim}
position(R,C,T-1,A+1) 		:- solving_conflict(R',T,A), isRobot(robot(R)), position(R,C,T-1,A).
move(R,D,T',A+1) 			:- solving_conflict(R',T,A), isRobot(robot(R)), R!=R', move(R,D,T',A), T'>=T.
\end{verbatim}
The first rule raises the conflict depth of the position predicate of every robot in the time step before the conflict. The second rule raises the conflict depth of every move predicate of every robot, except the selected one, in every time step after the conflict. This way only the predicates from the time step of the conflict and after that get changed. This reduces the memory needed compared to always changing all the predicates including the ones before the conflict happened. \\
The only thing left is to change the plan of the selected robot accordingly. Since there are two possible solutions for a conflict, there are two ways to push back the plan. The first possible solution is that the robot waits. In this case the plan only needs to get pushed back by one time step:
\begin{verbatim}
move(R,D,T'+1,A+1) 			:- solving_conflict(R,T,A), not move(R,_,T,A+1), move(R,D,T',A), T'>=T, time(T').
\end{verbatim}
The second possibility is that the robot moves into a random direction. If this is the case, the robot has to move into the opposite direction to be able to reach his goal position. The problem is that it is hard to decide at which time step the robot goes back since there could be new problems if it moves back at a time where there is already an occupied node which creates new conflicts. This is why, I let the solver decide at which time step the robot moves back:
\begin{verbatim}
1{step_back(R,(DX',DY'),T_B,A+1) : time(T_B), T_B<=horizon, T_B>T}1:- solving_conflict(R,T,A), move(R,(DX,DY),T,A+1), DX'=-DX, DY'=-DY.
\end{verbatim}
This rule chooses a time step between the conflict and the horizon where the robot moves into the opposite direction of the dodge move. After that the plan of the robot gets raised in conflict depth while changing the time steps accordingly:
\begin{verbatim}
move(R,D,T,A) :- step_back(R,D,T,A).
move(R,D,T'+1,A+1) 			:- solving_conflict(R,T,A), step_back(R,_,T_B,A+1), move(R,D,T',A), T'>=T, T<T_B-1.
move(R,D,T'+2,A+1) 			:- step_back(R,_,T_B,A+1), move(R,D,T',A), T'>=T_B-1.
\end{verbatim}
Since there are two rules in which the solver randomly decides which action to take, it is of advantage again to let the solver minimize the arising conflicts. This way the chosen actions result in the smallest number of conflicts.

\subsection{Integrity Constraints}
There are several integrity constraints used to ensure the correctness of the program as well as reducing the solution time.
These constraints only check if the predicates move out of the domain:
\begin{verbatim}
:- move(_,_,T,_), T>horizon.
:- position(_,_,T,_), T>horizon.
:- move(_,_,_,A), A>c_nr.
:- position (_,_,_,A), A>c_nr.
:- conflict(_,T,_), T>=horizon.
:- conflict(_,_,A), A>=c_nr.
\end{verbatim}
The conflict predicate cannot have $horizon$ or $c\_nr$ itself as argument because if a conflict arises the plan needs to get changed again an the predicates would move out of bounds.

\subsection{Output}
The resulting plan should only take the predicate with the highest conflict depth in each time step. 
\begin{verbatim}
new_move(R,D,T) :- move(R,D,T,MAX_C), MAX_C == #max{A: position(R,C,T-1,A)}.
\end{verbatim}
The predicate $new\_move$ contains the moves that had the highest conflict depth. The highest conflict depth is determined by looking at the position before a move. Every time a conflict arises, the position before the conflict has its conflict depth raised. This means that the position predicate is always the latest. The move predicate cannot be used to determine the highest conflict depth because there is no move predicate if a robot is waiting. \\
The predicate $new\_move$ gets translated into a form resembling the original input:
\begin{verbatim}
new_occurs(object(robot,R),action(move,D),T) :- new_move(R,D,T).
\end{verbatim}
The solver shows the $new\_occurs$ predicate as its solution.

\subsection{Extra Features}
There are two extra features I have dealt with. The first extra feature is the possibility of declaring that certain robots do not have to change their plan at all.
This is done by adding the predicate $strict\_plan(R\_ID)$ with $R\_ID$ being the ID of a robot. The only thing that gets changed in the encoding is in the conflict detection part:
\begin{verbatim}
conflict(R1,T,A) :- position(R1,C1,T-1,A), position(R1,C2,T,A), position(R2,C2,T,A), 
                    R1!=R2, conflict_nr(A), not strict_plan(R1).
\end{verbatim}
The only things that gets added is that a robot can only have a conflict that he might have to solve if he does not have the predicate $strict\_plan$. It is
the same for the second type of conflict. If two robots have a conflict and they both have strict plans there is no solution for that particular problem. 
This is encoded by using additional integrity constraints:
\begin{verbatim}
:- position(R1,C1,T-1,A), position(R1,C2,T,A), position(R2,C2,T,A), R1!=R2, 
   conflict_nr(A), strict_plan(R1), strict_plan(R2).
\end{verbatim}
The other conflict type looks the same. As this is a very hard constraint and can very easily lead to unsatisfiable problems, I have decided to expend on the idea
to let the user control which robot gets chosen as the one who has to solve the conflict. This brings me to my second feature: Introducing a priority system.
The user can add predicates $priority(R\_ID, P)$ where $R\_ID$ is the ID of a robot again and P is the assigned priority of that robot. 
The solver then always chooses the robot with the lower priority to solve a conflict. If two robots have the same priority, either can be chosen. 
\begin{verbatim}
conflict(R1,T,A) :- position(R1,C1,T-1,A), position(R1,C2,T,A), position(R2,C2,T,A), 
                    R1!=R2, conflict_nr(A), p_priority(R1,P1), 
                    p_priority(R2,P2), P1<=P2.
p_priority(R,P) :- priority(R,P).
p_priority(R,0) :- not priority(R,_), isRobot(robot(R)).						
\end{verbatim}
The second conflict looks like the first one. The reason I change $priority$ to $p\_priority$ is that this way I can introduce a default value. If the user does not choose any priority value for a robot,
the priority gets set to 0. \\
Both features change how the conflict solving robot is chosen. Using them can be useful in certain scenarios, especially the second one, but it should be noted that those features can
easily make an instance unsatisfiable.

\section{Analysis of Solution}
There are several benchmarks the solution has been tested on a (a complete list can be found in the appendix). By looking at the results it is obvious that the presented solution is very time inefficient. While it is fast when there is only a small number of robots, a small $horizon$ and a small $c\_nr$, the solution gets very high very fast when these parameters are rising. It does not seem like there is a specific parameter that affects the time the most but that the time rises a lot as soon as there are at least 2 parameters rising. This time inefficiency was not entirely unexpected. There are several problems that result in this time inefficiency. The first one is that there are two domains whose upper bound are determined by a constant that is chosen at run-time. Especially the usage of the conflict depth makes it very inefficient. Every time there is a conflict, the whole remaining plan has to get pushed back. This results in a lot of predicates that need to be created. Another problematic part is the inertia rule. Since it has to check for every possible time step, conflict depth and robot whether there is a move predicate, it gets very inefficient. However, I have found no way to avoid this problem. \\
Another part that makes the solution inefficient is the usage of choice rules. Since there are several rules where the solver can decide which to choose, a lot of possibilities get created. However, this way of solving has the advantage that theoretically all problems can be solved. In practice, there is only one instance that was not solvable\footnote{Benchmark: Limited Moves by Marius and Niklas}. I have also created a similar benchmark\footnote{Benchmark: Instance 6} which basically deals with the same problem. The solver could solve this benchmark which means that there is another problem with the unsolvable instance that I could not find. Since it is likely a very niche problem instance, it is not too devastating that it is unsolvable. \\
To summarize, the solution is time inefficient but generally usable. To avoid a high solution time, the instances should be broken down to ones that only need smaller parameters. For example, big instances could be divided into smaller groups which get solved. After that these plans get combined again to form the complete plan. Another possible application case is already having a plan for a lot of robots and just adding a small number of robots. In both cases, the conflict number might be lower which would allow the solver to find a solution in an acceptable time frame.

\section{Comparison with other approaches}
 - advantages and disadvantages of my approach compared to other approaches based on the benchmarking

\section{Conclusion}
This paper explained my approach on how to solve the plan merging problem for the asprilo framework. The solution is able to solve almost all of the benchmarks with the exception being a very niche 
benchmark that is unlikely to appear in the real world. There are two main problems in my solution. The first is that it is very time inefficient. The second is that the user has to in put the time horizon and
the maximum conflict number. If he does not know it, he will likely take an upper bound which increases the computation time. While those two problems are definitely a major deficit of my solution, the trade-off
is that it is generally usable and it finds a solution with the minimum amount of conflicts needed to solve a problem instance. To avoid the time inefficiency, the user can also take a parallel approach, i.e. combining 
the plans of 2 robots at a time, then combining these plans again and so on. This way, the conflict number of the problem instances is likely lower than when combining all plans at once. This also means that the computation time
is reduced. Another possible usage of this solution is adding new robots to a warehouse where a plan for the other robots already exists. Since only a small number of robots is likely added, the conflict number is probably low
enough to get a solution in an acceptable time. \\
My solution to solving the plan merging problem has a lot of possibilities of getting improved, like time efficiency and taking it to the A-domain of the framework. Nevertheless, it is an approach that solves the problem and could
be used in certain scenarios.

\newpage

\begin{thebibliography} {6}
\bibitem{asprilo}
asprilo framework
\begin{verbatim}
https://asprilo.github.io/
\end{verbatim}

\bibitem{owngithub}
My Github Repository
\begin{verbatim}
https://github.com/salewsky/Plan-Merging
\end{verbatim}

\bibitem{github1}
Github Repository of Tarek Ramadan
\begin{verbatim}
https://github.com/tramadan-up/asprilo-project
\end{verbatim}

\bibitem{github2}
Github Repository of Tom Schmidt, Hannes Weichelt and Julian Bruns
\begin{verbatim}
https://github.com/tzschmidt/PlanMerger
\end{verbatim}

\bibitem{github3}
Github Repository of Marcus Funke and Maximilian Wiedenhöft
\begin{verbatim}
https://github.com/Zard0c/ProjektMAPF
\end{verbatim}

\bibitem{github4}
Github Repository of Marius Wawerek and Niklas Kämmer
\begin{verbatim}
https://github.com/NikKaem/mapf-project
\end{verbatim}

\end{thebibliography}

\end{document}

### 2021-03-11 Documentation/paper.tex
Updated Documentation

@@
 \begin{document}
-\title{Merging Plans of Robots in the asprilo Framework}
-
-\author{Adrian Salewsky}
-
-\authorrunning{A. Salewsky}
-
-\institute{University of Potsdam}
-
-\maketitle
+\begin{titlepage}
+\centering
+{\scshape\LARGE University of Potsdam \par}
+\vspace{1cm}
+{\scshape\Large Project in Computational Intelligence\par}
+\vspace{1.5cm}
+{\huge\bfseries Merging Robot Plans in the asprilo framework\par}
+\vspace{2cm}
+{\Large\itshape Adrian Salewsky\par}
+\vfill
+supervised by\par
+Etienne Tignon
+\vfill
+{24.03.2021 \par}
 
@@
 \end{abstract}
+\end{titlepage}
 
@@
 the positions of objects contain an argument $T$ which declares at which time step the predicate holds. This project was done in the M-domain of the asprilo framework.
-In the M-domain, the goal is that every shelf has a robot on the same node at the last time step (the last time step is called horizon). This domain simplifies the framework 
+In the M-domain, the goal is to have a robot under each shelf that contains an ordered product at the last time step (the last time step is called horizon). This domain simplifies the framework 
 to Multi-Agent Path Finding (MAPF). The framework works well for a small number of robots but for a high number of robots, the computation time gets too high. This is
-why the plan came up to combine plans with a small number of robots to a plan with all the robots. During the combining of these plans, all the conflicts that arise between 
+why the plan came up to combine plans for a small number of robots to a plan for all the robots. During the combining of these plans, all the conflicts that arise between 
 robots must be solved. This paper shows my approach on how to solve this plan merging problem in ASP. In the following section, I will show my general idea on how to solve 
-conflicts. In the section after that, I will show my ASP encoding and explain its functions. Section 4 contains the comparison of my approach with that of other groups that have
-been working on the same project. I will end my paper with a conclusion.
+conflicts.
+In the section after that, I will show my ASP encoding and explain its functions.
+Section 4 contains the analysis on the efficiency of my solution.
+The comparison of my approach with that of other groups that have
+been working on the same project is shown in section 5. I will end my paper with a conclusion.
 
 \section{Idea}
-The main idea behind my solution is that every time a conflict arises, one of the robots participating in the conflict randomly changes his movement during that time step and pushes his original plan back.
+The main idea behind my solution is that every time a conflict arises, one of the robots participating in the conflict randomly changes its movement during that time step and pushes his original plan back.
 To do that, the program needs to detect the conflicts and choose a robot who has to solve the conflict by generating a new move. The problem that arises is that
@@
 \subsection{Pre-Required Predicates}
-To solve the problem there are several predicates needed before starting to look for predicates.
+To solve the problem there are several predicates needed before starting to solve the conflicts.
 There are two domain intervals whose upper bounds are constants: $time$ with the constant $horizon$ and $conflict\_nr$ with the constant $c\_nr$.
 The constants are chosen at run-time.
-\\ There are some predicates that have been taken over from the encoding for the asprilo framework: $isRobot(robot(R))$ to check if something is a robot, $position((X,Y))$ to check if the node (X,Y) exists, $direction((X,Y))$ declares the 4 directions a robot can go into and $nextto(C1,D,C2)$ states that you get from the node C1 to the node C2 if you into direction D.
+\\ There are some predicates that have been taken over from the encoding for the asprilo framework: $isRobot(robot(R))$ to check if something is a robot, $position((X,Y))$ to check if the node (X,Y) exists, $direction((X,Y))$ declares the 4 directions a robot can go into and $nextto(C1,D,C2)$ states that you get from the node C1 to the node C2 if you move into direction D.
 \\
-The program expects as input a plan of the form $occurs(object(robot,R),action(move,D),T)$.
+As input, the program expects a plan of the form $occurs(object(robot,R),action(move,D),T)$.
 This is transformed into the predicate $move(R,D,T,0)$.
@@
                   :- move(R,D,T,A), position(R,C ,T-1,A), not nextto(C ,D,_).
-position(R,C,T,A) :- position(R,C,T-1,A), not move(R,_,T,A), conflict_nr(A), isRobot(robot(R)), time(T).
+position(R,C,T,A) :- position(R,C,T-1,A), not move(R,_,T,A), conflict_nr(A), 
+                     isRobot(robot(R)), time(T).
 \end{verbatim}
@@
 These rules declare that the last position of the initial plan is the goal position and that there can be no plan where a robot
-is not on his goal position at the end.
+is not on its goal position at the end.
 While this does not change the solution itself (the plan always only gets pushed back so the robot always ends on the same node), it improves the solution time.
@@
 There are two types of conflicts that can appear in a problem instance.
-The first one is that a robot arrives on a node which is either already occupied by another robot or another robot arrives in the same time step.
+The first one is that a robot arrives on a node which is either already occupied by another robot or another robot arrives in the same time step (see figures \ref{fig:c1_1} and \ref{fig:c1_2}).
+
+\begin{figure}
+   \begin{minipage}[b]{.4\linewidth} 
+      \includegraphics[width=\linewidth]{Images/Conflict 1_1}
+      \caption{Two robots arrive on the same node at the same time step.}
+      \label{fig:c1_1}
+   \end{minipage}
+   \hspace{.1\linewidth}
+   \begin{minipage}[b]{.4\linewidth} 
+      \includegraphics[width=\linewidth]{Images/Conflict 1_2}
+      \caption{A robot moves to an already occupied node.}
+      \label{fig:c1_2}
+   \end{minipage}
+\end{figure}
+
 \begin{verbatim}
-conflict(R1,T,A)	:- position(R1,C1,T-1,A), position(R1,C2,T,A), position(R2,C2,T,A), R1!=R2, conflict_nr(A).
+conflict(R1,T,A) :- position(R1,C1,T-1,A), position(R1,C2,T,A), 
+                    position(R2,C2,T,A), R1!=R2, conflict_nr(A).
 \end{verbatim}
 The predicate $conflict(R,T,A)$ is derived for the two robots participating in the conflict. \\
-The second conflict is two robots switching their places:
+The second conflict is two robots switching their places (see figure \ref{fig:c2}):
+
+\begin{figure}[h]
+\includegraphics[width=75mm]{Images/Conflict 2}
+\caption{Two robots switch places.}
+\label{fig:c2}
+\end{figure}
+
 \begin{verbatim}
-conflict(R1,T,A)	:- position(R1,C1,T-1,A), position(R1,C2,T,A), position(R2,C2,T-1,A), position(R2,C1,T,A),
+conflict(R1,T,A) :- position(R1,C1,T-1,A), position(R1,C2,T,A), 
+                    position(R2,C2,T-1,A), position(R2,C1,T,A), 
                     R1!=R2, conflict_nr(A).
@@
 The program detects all of the conflicts arising in a plan this way.
-Only one conflict can get solved in each conflict depth, otherwise separate plans get created for each robots.
+Only one conflict can get solved in each conflict depth, otherwise separate plans get created for each robot because there would be a separate plan to solve each conflict.
 The program chooses one of the conflicts that appeared the earliest.
@@
 \begin{verbatim}
-0{move(R,D,T,A+1) : direction(D), nextto(C,D,_)}1 :- solving_conflict(R,T,A), position(R,C,T-1,A).
+0{move(R,D,T,A+1) : direction(D), nextto(C,D,_)}1 :- 
+                  solving_conflict(R,T,A), position(R,C,T-1,A).
 \end{verbatim}
@@
 \begin{verbatim}
-position(R,C,T-1,A+1) 		:- solving_conflict(R',T,A), isRobot(robot(R)), position(R,C,T-1,A).
-move(R,D,T',A+1) 			:- solving_conflict(R',T,A), isRobot(robot(R)), R!=R', move(R,D,T',A), T'>=T.
+position(R,C,T-1,A+1) :- solving_conflict(R',T,A), isRobot(robot(R)),
+                         position(R,C,T-1,A).
+move(R,D,T',A+1) :- solving_conflict(R',T,A), isRobot(robot(R)), R!=R', 
+                    move(R,D,T',A), T'>=T.
 \end{verbatim}
@@
 This way only the predicates from the time step of the conflict and after that get changed.
-This reduces the memory needed compared to always changing all the predicates including the ones before the conflict happened.
+This reduces the amount of predicates compared to always changing all the predicates including the ones before the conflict happened.
 \\
@@
 \begin{verbatim}
-move(R,D,T'+1,A+1) 			:- solving_conflict(R,T,A), not move(R,_,T,A+1), move(R,D,T',A), T'>=T, time(T').
+move(R,D,T'+1,A+1) :- solving_conflict(R,T,A), not move(R,_,T,A+1), 
+                      move(R,D,T',A), T'>=T, time(T').
 \end{verbatim}
 The second possibility is that the robot moves into a random direction.
-If this is the case, the robot has to move into the opposite direction to be able to reach his goal position.
+If this is the case, the robot has to move into the opposite direction to be able to reach its goal position.
 The problem is that it is hard to decide at which time step the robot goes back since there could be new problems if it moves back at a time where there is already an occupied node which creates new conflicts.
@@
 \begin{verbatim}
-1{step_back(R,(DX',DY'),T_B,A+1) : time(T_B), T_B<=horizon, T_B>T}1:- solving_conflict(R,T,A), move(R,(DX,DY),T,A+1), DX'=-DX, DY'=-DY.
+1{step_back(R,(DX',DY'),T_B,A+1) : time(T_B), T_B<=horizon, T_B>T}1:- 
+        solving_conflict(R,T,A), move(R,(DX,DY),T,A+1), DX'=-DX, DY'=-DY.
 \end{verbatim}
 This rule chooses a time step between the conflict and the horizon where the robot moves into the opposite direction of the dodge move.
-After that the plan of the robot gets raised in conflict depth while changing the time steps accordingly:
+After that, the plan of the robot gets raised in conflict depth while changing the time steps accordingly:
 \begin{verbatim}
 move(R,D,T,A) :- step_back(R,D,T,A).
-move(R,D,T'+1,A+1) 			:- solving_conflict(R,T,A), step_back(R,_,T_B,A+1), move(R,D,T',A), T'>=T, T<T_B-1.
+move(R,D,T'+1,A+1) :- solving_conflict(R,T,A), step_back(R,_,T_B,A+1), 
+                      move(R,D,T',A), T'>=T, T<T_B-1.
 move(R,D,T'+2,A+1) :- step_back(R,_,T_B,A+1), move(R,D,T',A), T'>=T_B-1.
@@
 \end{verbatim}
-The conflict predicate cannot have $horizon$ or $c\_nr$ itself as argument because if a conflict arises the plan needs to get changed again an the predicates would move out of bounds.
+The conflict predicate cannot have $horizon$ or $c\_nr$ itself as argument because if a conflict arises the plan needs to get changed again and the predicates would move out of bounds.
 
@@
 \end{verbatim}
-The solver shows the $new\_occurs$ predicate as its solution.
+The solver shows the $new\_occurs$ predicates as its solution.
 
@@
 \end{verbatim}
-The only things that gets added is that a robot can only have a conflict that he might have to solve if he does not have the predicate $strict\_plan$. It is
+The only things that gets added is that a robot can only have a conflict that it might have to solve if it does not have the predicate $strict\_plan$. It is
 the same for the second type of conflict. If two robots have a conflict and they both have strict plans there is no solution for that particular problem. 
@@
 \end{verbatim}
-The other conflict type looks the same. As this is a very hard constraint and can very easily lead to unsatisfiable problems, I have decided to expend on the idea
+The other conflict type looks the same. As this is a very hard constraint and can very easily lead to unsatisfiable problems, I have decided to extend the idea
 to let the user control which robot gets chosen as the one who has to solve the conflict. This brings me to my second feature: Introducing a priority system.
@@
 
-\section{Comparison with other approaches}
+\section{Comparison with other Approaches}
  - advantages and disadvantages of my approach compared to other approaches based on the benchmarking
@@
 The first is that it is very time inefficient.
-The second is that the user has to in put the time horizon and
+The second is that the user has to input the time horizon and
 the maximum conflict number.
@@
 
+\newpage
+\appendix
+\section{Benchmark Results}
+\begin{tabular}[h]{c|c|c|c|c|c}
+Instance & Time & CPU-Time & Horizon & Solved Conflicts & Robots \\
+Instance 1 & 0.125s & 0.109s & 5 & 1 & 2 \\
+Instance 2 & 5.063s & 5.016s & 10 & 3 & 4 \\
+Instance 3 & 2.672s & 2.641s & 9 & 2 & 4 \\
+Instance 4 & 0.078s & 0.078s & 2 & 0 & 4 \\
+Instance 5 & 0.484s & 0.469s & 4 & 3 & 4 \\
+Instance 6 & 696.239s & 695.594s & 14 & 9 & 2 \\
+Instance 7 & 134.847s & 134.672 & 9 & 3 & 8 \\
+\end{tabular}
+
 \end{document}

### 2021-03-17 Documentation/paper.tex
Benchmarking and Documentation

@@
 \section{Introduction}
-The asprilo framework is used to make plans for robots in a warehouse, i.e. when does a robot pick up or shelf or when does a robot move which way. 
+The asprilo framework is used to make plans for robots in a warehouse, i.e. when does a robot pick up or shelf or when does a robot move which way \cite{asprilo}. 
 It uses the language Answer Set Programming (ASP). Since there is no order in which ASP computes things, the predicates which describe the actions of robots and
@@
 to Multi-Agent Path Finding (MAPF). The framework works well for a small number of robots but for a high number of robots, the computation time gets too high. This is
-why the plan came up to combine plans for a small number of robots to a plan for all the robots. During the combining of these plans, all the conflicts that arise between 
-robots must be solved. This paper shows my approach on how to solve this plan merging problem in ASP. In the following section, I will show my general idea on how to solve 
+why the idea came up to combine plans for a small number of robots to a plan for all the robots. During the combining of these plans, all the conflicts that arise between 
+robots must be solved.
+This paper shows my approach on how to solve this plan merging problem in ASP.
+The solver I used is ``clingo 5.4.0''.In the following section, I will show my general idea on how to solve
 conflicts.
@@
 The comparison of my approach with that of other groups that have
-been working on the same project is shown in section 5. I will end my paper with a conclusion.
+been working on the same project is shown in section 5. I will end my paper with a conclusion. \\
+My solution as well as the used benchmarks can be found in my github repository \cite{owngithub}.
 
@@
 This idea is a very simple approach to solving the problem since it completely adapts the original plan and only
-inserts additional moves. This way the resulting solution might not have an optimal move set for every robot but it should be able to theoretically solve any problem instance.
+inserts additional moves. This way the resulting solution might not have an optimal move set for every robot but it should be able to theoretically solve most problem instances.
 
@@
 \subsection{Pre-Required Predicates}
-To solve the problem there are several predicates needed before starting to solve the conflicts.
-There are two domain intervals whose upper bounds are constants: $time$ with the constant $horizon$ and $conflict\_nr$ with the constant $c\_nr$.
+To solve the problem, there are several predicates needed before starting to solve the conflicts.
+There are two domain intervals whose upper bounds are constants: $time$, which states at which time step something happens, with the constant $horizon$ and $conflict\_nr$, which states how many conflicts have been solved to reach this plan, with the constant $c\_nr$.
 The constants are chosen at run-time.
@@
 The program detects all of the conflicts arising in a plan this way.
-Only one conflict can get solved in each conflict depth, otherwise separate plans get created for each robot because there would be a separate plan to solve each conflict.
+Only one conflict can get solved in each conflict depth, otherwise multiple plans get created for each robot because there would be separate plans to solve each conflict.
 The program chooses one of the conflicts that appeared the earliest.
@@
 The second rule raises the conflict depth of every move predicate of every robot, except the selected one, in every time step after the conflict.
-This way only the predicates from the time step of the conflict and after that get changed.
+This way only the predicates starting from the time step of the conflict get changed.
 This reduces the amount of predicates compared to always changing all the predicates including the ones before the conflict happened.
@@
 \end{verbatim}
-The other conflict type looks the same. As this is a very hard constraint and can very easily lead to unsatisfiable problems, I have decided to extend the idea
+The other conflict type looks the same. As this is a very strong constraint and can very easily lead to unsatisfiable problems, I have decided to extend the idea
 to let the user control which robot gets chosen as the one who has to solve the conflict. This brings me to my second feature: Introducing a priority system.
@@
 It does not seem like there is a specific parameter that affects the time the most but that the time rises a lot as soon as there are at least 2 parameters rising.
-This time inefficiency was not entirely unexpected.
+\\
 There are several problems that result in this time inefficiency.
-The first one is that there are two domains whose upper bound are determined by a constant that is chosen at run-time.
+The first one is that there are two domains whose upper bounds are determined by constants that are chosen at run-time.
 Especially the usage of the conflict depth makes it very inefficient.
@@
 Since there are several rules where the solver can decide which to choose, a lot of possibilities get created.
-However, this way of solving has the advantage that theoretically all problems can be solved.
-In practice, there is only one instance that was not solvable\footnote{Benchmark: Limited Moves by Marius and Niklas}.
-I have also created a similar benchmark\footnote{Benchmark: Instance 6} which basically deals with the same problem.
-The solver could solve this benchmark which means that there is another problem with the unsolvable instance that I could not find.
-Since it is likely a very niche problem instance, it is not too devastating that it is unsolvable.
+However, this way of solving has the advantage that theoretically most problems can be solved.
+There are three benchmarks that took too long\footnote{The upper time limit I chose is half an hour} to solve.
+Two of them have a high number of robots (50 and 30) and need a high horizon as well (about 30 and 60 respectively).
+The third one only has two robots but a $horizon$ of 19 and a $c\_nr$ of 10.
+This shows that all the parameters greatly influence the solution time.
 \\
-To summarize, the solution is time inefficient but generally usable.
-To avoid a high solution time, the instances should be broken down to ones that only need smaller parameters.
-For example, big instances could be divided into smaller groups which get solved.
-After that these plans get combined again to form the complete plan.
-Another possible application case is already having a plan for a lot of robots and just adding a small number of robots.
-In both cases, the conflict number might be lower which would allow the solver to find a solution in an acceptable time frame.
+There are two benchmarks, where the solver returned ``unsatisfiable''.
+One of them has three robots in a circular corridor (see figure \ref{fig:I1}).
+This instance is not solvable because the robots need to discard their original plans.
+As my approach only delays the original plan, it cannot solve such instances.
+This instance is negligible since it is unlikely that there is a warehouse layout in the real world that does not have any extra space for the robots to dodge to.
+The second unsolvable instance can be seen in figure \ref{fig:I2}.
+I do not know why this instance is unsolvable.
+A similar instance is the one shown in figure \ref{fig:I3}.
+This instance basically deals with the same problem and can be solved with my solution.
+Even when reducing the unsolvable instance to just two robots, which makes it even more like the other instance, it is unsolvable.
+However, this problem seems to be negligible as well since the other benchmarks were solved as expected.
+This means that only problems that are unlikely to appear in the real world seem to be unsolvable.
+\\
+To summarize, my approach is time inefficient but it seems to be able to solve most problems.
+This means that it can be used for small instance where the parameters are not very high.
+The found solution is not optimal because it only solves a conflict the moment it occurs and always completely uses the original plan.
+
+\begin{figure}[h]
+\includegraphics[width=75mm]{Images/Instance 1}
+\caption{Benchmark\_1 by Tarek Ramadan}
+\label{fig:I1}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=75mm]{Images/Instance 2}
+\caption{Benchmark-5 by Marius W and Niklas K.}
+\label{fig:I2}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=75mm]{Images/Instance 3}
+\caption{Instance 6 (Own Benchmark)}
+\label{fig:I3}
+\end{figure}
 
 \section{Comparison with other Approaches}
- - advantages and disadvantages of my approach compared to other approaches based on the benchmarking
+There are 4 other groups that have worked on the same problem. In the appendix, the benchmark results of every solution can be found. \\
+The solution of Tarek Ramadan \cite{github1} is able to solve most instances in a short time.
+The instances with 30 and 50 robots take too long for his solution as well.
+There are two instances his approach could not solve.
+Both of these were solvable by my approach.
+This means, his approach is generally faster but has problems with different instances.
+\\
+The approach of Tom Schmidt, Hannes Weichelt and Julian Bruns \cite{github2} is very fast in the instances it can solve.
+It is the only approach that can solve the instances with 50 and 30 robots in the designated time frame.
+The downside is that there are three instances that are unsatisfiable.
+Benchmark\_1 (the circular shape) is one of them.
+Another unsolvable instance is the one where the robots have to move away from their original path together which seems to be a problem for this approach.
+The third unsatisfiable instance is a rather simple problem with only one conflict which makes it weird that it cannot be solved.
+After talking with the group it seems that they find a solution which makes this a rather strange problem.
+Apart from the unsolvable instances, there are two instances where the solver finds solutions in the given horizon but these solutions have one robot next to their goal node which makes the solution wrong.
+The approach of this group seems to be very fast.
+The downside to it is that it is unreliable since there are some unsolvable instances and the found solutions are not always correct.
+\\
+The solution of Marcus Funke and Maximilian Wiedenhöft \cite{github3} seems to have problems similar to mine.
+It is very time inefficient.
+Furthermore, there are three instances that cannot be solved.
+One of those instances is Benchmark\_1 which my approach could not solve either.
+Their solution can however solve the other instance mine could not.
+To summarize, their approach is time inefficient as well and there is a similar amount of instances it cannot solve.
+\\
+The solution of Marius Wawerek and Niklas Kämmer \cite{github4} has very short solution times for most instances.
+The only instances that could not be solved in the designated time were the ones with 30 and 50 robots.
+There is no instance that is unsolvable.
+It seems to be the best solution for solving small instances.
+There does not seem to be any instance it cannot solve.
+The only problem is that the solving time rises too high if there are too many robots.
 
 \section{Conclusion}
-This paper explained my approach on how to solve the plan merging problem for the asprilo framework. The solution is able to solve almost all of the benchmarks with the exception being a very niche 
-benchmark that is unlikely to appear in the real world.
+This paper explained my approach on how to solve the plan merging problem for the asprilo framework. The solution is able to solve almost all of the benchmarks with the exception being two very niche 
+benchmarks that are unlikely to appear in the real world.
 There are two main problems in my solution.
@@
 is that it is generally usable and it finds a solution with the minimum amount of conflicts needed to solve a problem instance. 
-To avoid the time inefficiency, the user can also take a parallel approach, i.e.
-combining
-the plans of 2 robots at a time, then combining these plans again and so on.
-This way, the conflict number of the problem instances is likely lower than when combining all plans at once.
-This also means that the computation time
-is reduced.
-Another possible usage of this solution is adding new robots to a warehouse where a plan for the other robots already exists.
-Since only a small number of robots is likely added, the conflict number is probably low
-enough to get a solution in an acceptable time. \\
+This means that it can be used in small instances where there are not two many robots and a small amount of conflicts.\\
 My solution to solving the plan merging problem has a lot of possibilities of getting improved, like time efficiency and taking it to the A-domain of the framework.
@@
 \section{Benchmark Results}
-\begin{tabular}[h]{c|c|c|c|c|c}
+The solver was interrupted after a solving time of half an hour. If the solver needed more time than that,
+the solving time is shown as ``TOO LONG''.
+The solver did not find a solution if these instances were tested with smaller parameters.
+The instances that were ``UNSATISFIABLE'' are the ones that are unlikely to return a solution even when using
+higher parameters.
+
+\subsection{My Solver}
+\begin{tabular}[h]{l|c|c|c|c|c}
 Instance & Time & CPU-Time & Horizon & Solved Conflicts & Robots \\
 Instance 1 & 0.125s & 0.109s & 5 & 1 & 2 \\
-Instance 2 & 5.063s & 5.016s & 10 & 3 & 4 \\
-Instance 3 & 2.672s & 2.641s & 9 & 2 & 4 \\
-Instance 4 & 0.078s & 0.078s & 2 & 0 & 4 \\
 Instance 5 & 0.484s & 0.469s & 4 & 3 & 4 \\
@@
 Instance 7 & 134.847s & 134.672 & 9 & 3 & 8 \\
+bench\_test\_2 & 0.125s & 0.109s & 7 & 1 & 2 \\
+bench\_test\_3 & 0.078s & 0.063s & 4 & 1 & 2 \\
+bench\_test\_16\_mod1 & 11.220s & 10.922s & 8 & 5 & 4 \\
+Benchmark-5 & \multicolumn{2}{c|}{UNSATISFIABLE(1525s)} & 17 & 14 & 4 \\
+Benchmark-6 & 881.982s & 875.938s & 10 & 6 & 8 \\
+Benchmark-42 & 16.619s & 16.531s & 10 & 1 & 5 \\ 
+Benchmark-51 & 1702.764s & 1696.922s & 23 & 1 & 6 \\
+Benchmark 03 & 16.467s & 16.188s & 7 & 5 & 4 \\
+Benchmark 05 & 0.121s & 0.094s & 4 & 1 & 3 \\
+Benchmark R1 &\multicolumn{2}{c|}{TOO LONG} & 20 & 1 & 50 \\
+Benchmark R2 & \multicolumn{2}{c|}{TOO LONG} & 20 & 1 & 30 \\
+Benchmark\_1 & \multicolumn{2}{c|}{UNSATISFIABLE(355s)} & 8 & 8 & 3 \\ 
+Benchmark\_2 & \multicolumn{2}{c|}{TOO LONG} & 19 & 10 & 2 \\
+Benchmark\_3 & 1.075s & 1.063s & 9 & 2 & 3 \\
+Benchmark\_4 & 3.133s & 3.109s & 15 & 4 & 2 \\
+\end{tabular}
+
+\subsection{Tarek Ramadan}
+\begin{tabular}[h]{l|c|c|c|c|c}
+Instance & Time & CPU-Time & Horizon & Constant rm & Robots \\
+Instance 1 & 0.172s & 0.141s & 5 & 1 & 2 \\
+Instance 5 & \multicolumn{2}{c|}{UNSATISFIABLE(0.06s)} & - & 10 & 4 \\
+Instance 6 & 0.246s & 0.234s & 14 & 9 & 2 \\
+Instance 7 & \multicolumn{2}{c|}{UNSATISFIABLE(5.88s)} & - & 10 & 8 \\
+bench\_test\_2 & 0.159s & 0.109s & 5 & 2 & 2 \\
+bench\_test\_3 & 0.134s & 0.125s & 4 & 3 & 2 \\
+bench\_test\_16\_mod1 & 0.241s & 0.203s & 6 & 4 & 4 \\
+Benchmark-5 & 0.762s & 0.688s & 17 & 7 & 4 \\
+Benchmark-6 & 1.213s & 1.063s & 11 & 5 & 8 \\
+Benchmark-42 & 1.673s & 1.578s & 11 & 2 & 5 \\ 
+Benchmark-51 & 13.101s & 11.891s & 23 & 3 & 6 \\
+Benchmark 03 & 0.266s & 0.172s & 5 & 4 & 4 \\
+Benchmark 05 & 0.142s & 0.094s & 4 & 3 & 3 \\
+Benchmark R1 &\multicolumn{2}{c|}{TOO LONG} & - & 5 & 50 \\
+Benchmark R2 & \multicolumn{2}{c|}{TOO LONG} & - & 5 & 30 \\
+Benchmark\_1 & 0.219s & 0.156s & 5 & 4 & 3 \\ 
+Benchmark\_2 & 1.687s & 1.516s & 19 & 16 & 2 \\
+Benchmark\_3 & 0.904s & 0.734s & 14 & 6 & 3 \\
+Benchmark\_4 & 0.298s & 0.281s & 15 & 8 & 2 \\
+\end{tabular}
+
+\subsection{Tom Schmidt, Hannes Weichelt and Julian Bruns}
+Instance 7 and Benchmark-6 return a solution. In these solutions however, not all robots
+are on their goal node which means they are wrong. \\
+\\
+\begin{tabular}[h]{l|c|c|c}
+Instance & Solving Time & Horizon & Robots \\
+Instance 1 & 0.066s & 5 & 2 \\
+Instance 5 & 0.060s  & 3 & 4 \\
+Instance 6 & 0.110s & 8 & 2 \\
+Instance 7 & 0.710s  & 11 & 8 \\
+bench\_test\_2 & UNSATISFIABLE(60s) & 20 & 2 \\
+bench\_test\_3 & 0.071s & 6 & 2 \\
+bench\_test\_16\_mod1 & 0.231s & 8 & 4 \\
+Benchmark-5 & 0.474s & 13 & 4 \\
+Benchmark-6 & 2.157s & 12 & 8 \\
+Benchmark-42 & 0.112s & 11 & 5 \\ 
+Benchmark-51 & 1.712s & 23 & 6 \\
+Benchmark 03 & 0.192s & 7 & 4 \\
+Benchmark 05 & 0.045s & 5 & 3 \\
+Benchmark R1 & 278.224s & 29 & 50 \\
+Benchmark R2 & 255.805s & 62 & 30 \\
+Benchmark\_1 & UNSATISFIABLE(5s) & 15 & 3 \\ 
+Benchmark\_2 & UNSATISFIABLE(83s) & 25 & 2 \\
+Benchmark\_3 & 0.212s & 11 & 3 \\
+Benchmark\_4 & 0.437s & 15 & 2 \\
+\end{tabular}
+
+\subsection{Marcus Funke and Maximilian Wiedenhöft}
+\begin{tabular}[h]{l|c|c|c|c}
+Instance & Time & CPU-Time & Horizon &  Robots \\
+Instance 1 & 1.672s & 1.656s & 5 & 2 \\
+Instance 5 & \multicolumn{2}{c|}{UNSATISFIABLE(42s)} & 10 & 4 \\
+Instance 6 & 9.947s & 9.766s & 14 & 2 \\
+Instance 7 & \multicolumn{2}{c|}{TOO LONG} & 9  & 8 \\
+bench\_test\_2 & 3.361s & 3.172s & 7 & 2 \\
+bench\_test\_3 & 0.437s & 0.422s & 4 & 2 \\
+bench\_test\_16\_mod1 & 20.751s & 20.703s & 9 & 4 \\
+Benchmark-5 & 1398.237s & 1347.656s & 17 & 4 \\
+Benchmark-6 & \multicolumn{2}{c|}{TOO LONG} & 13 & 8 \\
+Benchmark-42 & \multicolumn{2}{c|}{TOO LONG} & 10  & 5 \\ 
+Benchmark-51 & \multicolumn{2}{c|}{TOO LONG} & 23 & 6 \\
+Benchmark 03 & 22.019s & 21.438s & 7 & 4 \\
+Benchmark 05 & 0.547s & 0.531s & 4 & 3 \\
+Benchmark R1 &\multicolumn{2}{c|}{TOO LONG} & 25 & 50 \\
+Benchmark R2 & \multicolumn{2}{c|}{TOO LONG} & 25 & 30 \\
+Benchmark\_1 & \multicolumn{2}{c|}{UNSATISFIABLE(5s)} & 10 & 3 \\ 
+Benchmark\_2 & \multicolumn{2}{c|}{UNSATISFIABLE(56s)} & 25 & 2 \\
+Benchmark\_3 & 92.768s & 92.250s & 10 & 3 \\
+Benchmark\_4 & 26.482s & 26.422s & 16 & 2 \\
+\end{tabular}
+
+\subsection{Marius Wawerek and Niklas Kämmer}
+\begin{tabular}[h]{l|c|c|c}
+Instance & Solving Time & Horizon & Robots \\
+Instance 1 & 0.049s & 5 & 2 \\
+Instance 5 & 0.060s  & 3 & 4 \\
+Instance 6 & 0.065s & 6 & 2 \\
+Instance 7 & 0.517s  & 9 & 8 \\
+bench\_test\_2 & 0.064s & 5 & 2 \\
+bench\_test\_3 & 0.046s & 4 & 2 \\
+bench\_test\_16\_mod1 & 0.075s & 6 & 4 \\
+Benchmark-5 & 0.794s & 11 & 4 \\
+Benchmark-6 & 0.534s & 9 & 8 \\
+Benchmark-42 & 0.723s & 10 & 5 \\ 
+Benchmark-51 & 0.577s & 21 & 6 \\
+Benchmark 03 & 0.078s & 5 & 4 \\
+Benchmark 05 & 0.038s & 4 & 3 \\
+Benchmark R1 & TOO LONG & 31 & 50 \\
+Benchmark R2 & TOO LONG & 57 & 30 \\
+Benchmark\_1 & 0.087 & 7 & 3 \\ 
+Benchmark\_2 & 1.575s & 19 & 2 \\
+Benchmark\_3 & 0.201s & 9 & 3 \\
+Benchmark\_4 & 0.269s & 15 & 2 \\
 \end{tabular}

### 2021-03-17 Benchmarks for Comparison/Tom S, Julian B, Hannes W/main.py

@@ -1,0 +1,157 @@
+import sys
+import os
+import warnings
+import time
+import clingo
+
+__author__ = "Hannes Weichelt"
+__credits__ = ["Hannes Weichelt", "Tom Schmidt", "Julian Bruhns"]
+__license__ = "GPL"
+__version__ = "1.0.1"
+__maintainer__ = "Hannes Weichelt"
+__email__ = "hweichelt@uni-postdam.de"
+__status__ = "Development"
+
+# cannot be 'occurs'
+original_occurs_format = 'occurs1'
+merger_file_name = 'merger.lp'
+
+
+def get_input_param_files():
+    if sys.argv:
+        files = []
+        for x in sys.argv:
+            if '.lp' in x:
+                if os.path.isfile(x):
+                    f = open(x, "r")
+                    files.append(f.read())
+                    f.close()
+                else:
+                    warnings.warn(f"WARNING: File '{x}' couldn't be found (import is skipped)")
+    return files
+
+
+def get_merger_content():
+    script_path = os.path.dirname(os.path.abspath(__file__))
+    print(f"load merger from : {script_path}/{merger_file_name}")
+    f = open(f"{script_path}/{merger_file_name}", "r")
+    merger_content = f.read()
+    f.close()
+    return merger_content
+
+
+def get_max_horizon(full_files_string):
+    curr_horizon = None
+    for line in full_files_string.split('\n'):
+        if '#const horizon' in line:
+            horizon_str = line.split('=')[1].split('.')[0].strip()
+
+            # check if the horizon statement format is correct
+            try:
+                horizon = int(horizon_str)
+            except ValueError:
+                raise ValueError(f"Invalid horizon format in line : '{line}'")
+
+            # check if there are multiple conflicting horizon statements in files
+            if curr_horizon:
+                if curr_horizon != horizon:
+                    raise ValueError(f"Two different horizon statements were found in files with the values:"
+                                     f"'{horizon}', '{curr_horizon}'")
+
+            # set the current detected horizon to the found valid horizon
+            curr_horizon = horizon
+
+    if curr_horizon:
+        return curr_horizon
+    else:
+        raise ValueError("No horizon constant found in input files. Please define the constant '#const horizon=n.' in "
+                         "your benchmark instance file.")
+
+
+def contains_plans(full_files_string):
+    for line in full_files_string.split('\n'):
+        if line.startswith(original_occurs_format):
+            return True
+    return False
+
+
[…]

### 2021-03-19 Documentation/paper.tex
Updated Documentation
Updated Benchmarking and Documentation

@@
 \vfill
-{24.03.2021 \par}
+{23.03.2021 \par}
 
 \begin{abstract}
-The asprilo framework was created to make plans for robots in a warehouse. It uses the language Answer Set Programming
-which is a good choice for such a problem because this language was made for solving NP-hard problems. The solution works 
-well for a small number of robots but at some point the computation time gets too high. This is why the idea came up to create plans
-for a small number of robots and then combine the plans to get a working solution. This paper shows my approach on how to solve
-the plan merging problem.
+This paper shows my approach to solving the plan merging problem in multi-agent path finding.
+This means that plans for single robots are combined to a plan for all robots.
+During the merging, all arising conflicts must be dealt with.
+This was done for a project
+at the University of Potsdam in the course Computational Intelligence for the chair Computational Intelligence.
+The project was done in the asprilo framework with the programming language Answer Set Programming.
 \end{abstract}
@@
 \section{Introduction}
-The asprilo framework is used to make plans for robots in a warehouse, i.e. when does a robot pick up or shelf or when does a robot move which way \cite{asprilo}. 
-It uses the language Answer Set Programming (ASP). Since there is no order in which ASP computes things, the predicates which describe the actions of robots and
-the positions of objects contain an argument $T$ which declares at which time step the predicate holds. This project was done in the M-domain of the asprilo framework.
-In the M-domain, the goal is to have a robot under each shelf that contains an ordered product at the last time step (the last time step is called horizon). This domain simplifies the framework 
-to Multi-Agent Path Finding (MAPF). The framework works well for a small number of robots but for a high number of robots, the computation time gets too high. This is
-why the idea came up to combine plans for a small number of robots to a plan for all the robots. During the combining of these plans, all the conflicts that arise between 
-robots must be solved.
-This paper shows my approach on how to solve this plan merging problem in ASP.
-The solver I used is ``clingo 5.4.0''.In the following section, I will show my general idea on how to solve
-conflicts.
-In the section after that, I will show my ASP encoding and explain its functions.
-Section 4 contains the analysis on the efficiency of my solution.
-The comparison of my approach with that of other groups that have
-been working on the same project is shown in section 5. I will end my paper with a conclusion. \\
+The multi-agent path finding (MAPF) problem deals with multiple agents that have to find their way to a goal.
+This paper deals with the problem of having plans for single robots and combining them to a plan that contains all robots.
+During the merging of the plans, arising conflicts must be solved.
+The solution presented in this paper uses the asprilo framework by potassco \cite{asprilo}, the language Answer Set Programming (ASP) and the solver clingo 5.4.0.
+More details on the asprilo framework will be given in the next section.
+Section 3 contains my idea on how to theoretically solve the plan merging problem.
+In the section after that, I will show my ASP encoding.
+Sections 5 and 6 contain the analysis of my solution as well as comparing my approach to approaches of other groups that have worked on the same problem.
+I will end my paper with a conclusion.
 My solution as well as the used benchmarks can be found in my github repository \cite{owngithub}.
+
+\section{The asprilo framework}
+The asprilo framework deals with robots in a warehouse.
+The framework has several domains.
+The ``M-Domain'' is the one that simplifies the problem to MAPF.
+The goal is that at the last time step (called horizon) all shelves containing an ordered product have a robot under them.
+This is done by finding plans for the robots in which they move to a shelf in the designated time.
+The asprilo framework uses ASP.
+This means the plans are created by using predicates and rules.
+The predicate stating when and how a robot moves is $move(R,D,T)$ with R being the robot, D being the direction it moves in and T being the time step at which the robot moves.
+To track the positions of robots the predicate $position(R,C,T)$ is used.
+R is the robot again, C is the node the robot is positioned on and T is the time step again.
+The $position$ predicate is also used for shelves.
+The resulting plan is shown in the form $occurs(object(robot,R),action(move,D),T)$.
+The arguments are the same as in the $move$ predicate.
+It is simply another form of representing them.
+\\
+There is also a visualizer for this framework. It is used to see how the found solution works. Images shown in this paper are screenshots taken from the visualizer.
+Since the plan merging problem uses the plans of single robots, the asprilo framework was used to create these plans. The visualizer was used to verify the correctness of the solutions.
 
@@
 \section{Comparison with other Approaches}
-There are 4 other groups that have worked on the same problem. In the appendix, the benchmark results of every solution can be found. \\
+There are 4 other groups that have worked on the same problem.
+In the appendix, the benchmark results of every solution can be found.
+For the group consisting of Marius Wawerek and Niklas Kämmer as well as the group consisting of Tom Schmidt, Hannes Weichelt and Jullian Bruns, I have used the python program created by the group of three.
+The program iteratively finds the minimal horizon for the used merger.
+\\
 The solution of Tarek Ramadan \cite{github1} is able to solve most instances in a short time.
@@
 The third unsatisfiable instance is a rather simple problem with only one conflict which makes it weird that it cannot be solved.
-After talking with the group it seems that they find a solution which makes this a rather strange problem.
-Apart from the unsolvable instances, there are two instances where the solver finds solutions in the given horizon but these solutions have one robot next to their goal node which makes the solution wrong.
 The approach of this group seems to be very fast.
-The downside to it is that it is unreliable since there are some unsolvable instances and the found solutions are not always correct.
+The downside to it is that it cannot solve some instances.
 \\
@@
 The instances that were ``UNSATISFIABLE'' are the ones that are unlikely to return a solution even when using
-higher parameters.
+higher parameters. ``Unlikely'' means that the approach the group took is not able to theoretically solve the instance.
 
@@
 \subsection{Tom Schmidt, Hannes Weichelt and Julian Bruns}
-Instance 7 and Benchmark-6 return a solution. In these solutions however, not all robots
-are on their goal node which means they are wrong. \\
-\\
 \begin{tabular}[h]{l|c|c|c}
@@
 Instance 6 & 0.110s & 8 & 2 \\
-Instance 7 & 0.710s  & 11 & 8 \\
+Instance 7 & 0.851s  & 10 & 8 \\
 bench\_test\_2 & UNSATISFIABLE(60s) & 20 & 2 \\
@@
 Benchmark-5 & 0.474s & 13 & 4 \\
-Benchmark-6 & 2.157s & 12 & 8 \\
+Benchmark-6 & 3.409s & 13 & 8 \\
 Benchmark-42 & 0.112s & 11 & 5 \\ 
@@
 Benchmark 05 & 0.045s & 5 & 3 \\
-Benchmark R1 & 278.224s & 29 & 50 \\
+Benchmark R1 & 184.887s & 23 & 50 \\
 Benchmark R2 & 255.805s & 62 & 30 \\
@@
 Benchmark 05 & 0.038s & 4 & 3 \\
-Benchmark R1 & TOO LONG & 31 & 50 \\
+Benchmark R1 & TOO LONG & 23 & 50 \\
 Benchmark R2 & TOO LONG & 57 & 30 \\

### 2021-03-20 Documentation/paper.tex
Finished Documentation, Updated Presentation

@@
 \section{Analysis of Solution}
-There are several benchmarks the solution has been tested on a (a complete list can be found in the appendix).
+There are several benchmarks the solution has been tested on (a complete list can be found in the appendix).
 By looking at the results it is obvious that the presented solution is very time inefficient.
-While it is fast when there is only a small number of robots, a small $horizon$ and a small $c\_nr$, the solution gets very high very fast when these parameters are rising.
+While it is fast when there is only a small number of robots, a small $horizon$ and a small $c\_nr$, the solution time gets very high very fast when these parameters are rising.
 It does not seem like there is a specific parameter that affects the time the most but that the time rises a lot as soon as there are at least 2 parameters rising.
@@
 To summarize, my approach is time inefficient but it seems to be able to solve most problems.
-This means that it can be used for small instance where the parameters are not very high.
+This means that it can be used for small instances where the parameters are not very high.
 The found solution is not optimal because it only solves a conflict the moment it occurs and always completely uses the original plan.
@@
 In the appendix, the benchmark results of every solution can be found.
-For the group consisting of Marius Wawerek and Niklas Kämmer as well as the group consisting of Tom Schmidt, Hannes Weichelt and Jullian Bruns, I have used the python program created by the group of three.
+For the group consisting of Marius Wawerek and Niklas Kämmer as well as the group consisting of Tom Schmidt, Hannes Weichelt and Julian Bruns, I have used the python program created by the group of three.
 The program iteratively finds the minimal horizon for the used merger.
